A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-03-05 manuscript.Rmd
add alternative codes of conduct

However, there is some controversy around how to handle violations of a code of conduct.
For that or any other reason, you may want to adapt the Contributor Covenant, to fit the needs of you project (which you are allowed to to because it is published with a CC-BY license).

@@

On your local machine, you use Git to track changes.
Online services like GitHub allow you to share these changes with others.
GitHub is not the only solution; there is also [GitLab](gitlab.com) or [BitBucket](https://bitbucket.org), which are as feature-rich as GitHub.
GitLab has the advantage that your institution can host it themselves; therefore, you are not relying on commercial service providers.
We focus on GitHub because it is the most popular service.
To upload your changes to GitHub, you need to create an account under https://github.com/join.
As a researcher, you are eligible for the `r link("https://help.github.com/en/articles/applying-for-an-educator-or-researcher-discount", "Researcher/Educator discount")`.
The following command creates a new GitHub repository under your GitHub account, beware this is public:
<!--Hands-on: Introduce Github-->

@@

A well defined "entry point" that automatically reproduces everything eases collaboration.

@@

>>>>

However, there is some controversy around how to handle violations of a code of conduct.
For that or any other reason, you may want to adapt the Contributor Covenant, to fit the needs of you project (which you are allowed to do because it is published with a CC-BY license).
You can also consider alternative Codes of Conduct, like the `r link("https://opensource.microsoft.com/codeofconduct/", "Microsoft Open Source Code of Conduct")` or the `r link("https://berlincodeofconduct.org", "Berlin Code of Conduct")`.

@@

On your local machine, you use Git to track changes.
Online services like GitHub allow you to share these changes with others.
GitHub is not the only solution; there is also [GitLab](gitlab.com) or [BitBucket](https://bitbucket.org), which are as feature-rich as GitHub.
GitLab has the advantage that your institution can host it themselves; therefore, you are not relying on commercial service providers.
Anyhow, we focus on GitHub because it is the most popular service.
To upload your changes to GitHub, you need to create an account under https://github.com/join.
As a researcher, you are eligible for the `r link("https://help.github.com/en/articles/applying-for-an-educator-or-researcher-discount", "Researcher/Educator discount")`.
The following command creates a new GitHub repository under your GitHub account, beware this is public:
<!--Hands-on: Introduce Github-->

@@

@@

First dependency management, which means that you capture the interrelations between the components of you analysis.
You cannot run an analysis without data, you cannot render a dynamic document without an analysis, and so forth.
Understanding these relations is often key to reproducing a project.
A reader of your reproducible manuscript should be able to derive how they are to reproduce it (ideally by a statement in your [README])
The "components" of an analysis are often loosely mapped onto files.
For a simple project it might be enough to have a single R Markdown.
However, while it is easy to reproduce this approach quickly gets unwieldy.
